---
title: "Google scholar"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r, include = FALSE}
library(scholar)
library(tidyverse)

# by default code is hidden on compilation
knitr::opts_chunk$set(echo = FALSE)
```


## define researcher

```{r}
## Define the id for Richard Feynman
id <- 'B7vSqZsAAAAJ'


## Get his profile
scholar_profile <- get_profile(id)

# what is contained in a profile?
str(scholar_profile)

## Print his name and affliation
scholar_profile$name
```



Report for scholar ID _`r id`_ with name of **`r scholar_profile$name`** from **`r scholar_profile$affiliation`**. They have a h-index of `r scholar_profile$h_index`.


- id         : chr "B7vSqZsAAAAJ"
- name       `r scholar_profile$name`
- affiliation: chr "California Institute of Technology"
- total_cites: num 92970
- h_index    : num 60
- i10_index  : num 94
- fields     : chr "no verified email"
- homepage   : chr(0) 
- coauthors  : chr ""

[scholar profile url](`r paste0("https://scholar.google.co.nz/citations?hl=en&user=",id)`)


## setup code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Vignette for the {scholar} package: https://cran.r-project.org/web/packages/scholar/vignettes/scholar.html

Before running the first time, we need to make sure the {scholar} package is installed. This only needs to be done once.
```{r, eval= FALSE}
install.packages("scholar")
```

Every time we open R or RStudio up we need to load the libraries that contain the functions that are additional to the functions that are included by default. I.e. the functions that are particular to this analysis.
```{r}
library(scholar)
library(tidyverse)
```

## Find Google Scholar ID



The example in the vignette was for Richard Feynman, but we need to get a google scholar ID to use the package. I did this by searching "Richard Feynman" in scholar.google.com and clicked through on the author profile. I then copied the url.


https://scholar.google.co.nz/citations?hl=en&user=B7vSqZsAAAAJ

Based on the API lesson we can look at the URL for the profile and the bit after 'user=' should be the ID; B7vSqZsAAAAJ

```{r}
## Define the id for Richard Feynman
id <- 'B7vSqZsAAAAJ'


## Get his profile
scholar_profile <- get_profile(id)

# what is contained in a profile?
str(scholar_profile)

## Print his name and affliation
scholar_profile$name
```

So this is telling us some information about the author that google scholar has.


We can also get information about his publications

```{r}
pubs <- get_publications(id)

```

## Citation History

We can retrieve information about his citation history

```{r}
## Get his citation history, i.e. citations to his work in a given year
ct <- get_citation_history(id)
```

What does the data we get back look like?

  ```{r}
head(ct)
```

We can visualise this information by plotting the number of cites (y) by year (x) to see if there is a trend.

```{r}
## Plot citation trend
ggplot(ct, aes(x = year, y = cites)) + geom_line() + geom_point()
```


## Most cited works


Table of most cited works

```{r}
pubs %>% select(title, journal, cites, year) %>% arrange(desc(cites)) %>% slice(1:15) %>% knitr::kable()
```

### History of most cited work

We can plot this information to see how citiations changed over time for this particular article

We can get the citation history for this particular article with get_article_cite_history(). We need to provide it the author id, and the publication id foe our article of choice
```{r}
## Get article citation history
article_cites <- get_article_cite_history(id, pubs$pubid[1])
```


```{r}
## Plot citation trend
ggplot(article_cites, aes(x = year, y = cites)) +
    geom_segment(aes(xend = year, yend = 0), size=1, color='darkgrey') +
    geom_point(size=3, color='firebrick')

```

## Network of co-authors

We can also visualise co-author networks

```{r}
coauthor_network <- get_coauthors('amYIKXQAAAAJ&hl', n_coauthors = 7)

coauthor_network
```

Plot the network
```{r}
plot_coauthors(coauthor_network)
```


A slightly different version of the plot is used in this example https://andreacontina.com/google-scholar/

