---
title: "Researcher Report"
author: "Murray Cadzow"
date: "07/08/2019"
output: 
  html_document:
    toc: yes
    toc_float: yes
params:
  id: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(scholar)
```

## About the researcher

```{r}
# id <- 'B7vSqZsAAAAJ' # Richard Fynman ID
#id <- "amYIKXQAAAAJ&hl"
id <- params$id
scholar_api_url <- "https://scholar.google.com/citations?hl=en&user="
scholar_profile <- get_profile(id)
```

The google scholar profile id is _`r id`_ and their name is **`r scholar_profile$name`** and their institue is: **`r scholar_profile$affiliation`**. Their H index (from google) is `r scholar_profile$h_index`.

### Researcher url

Their google scholar profile is [here](`r paste0(scholar_api_url, id)`) 



## Citation history

```{r}
## Get the authors citation history, i.e. citations to his work in a given year
ct <- get_citation_history(id)
```

```{r}
ggplot(data = ct, mapping = aes(x = year, y = cites)) + geom_line() + geom_point()
```

## Top 10 cited publications

```{r}
pubs <- get_publications(id)
```

This is a table of `r scholar_profile$name`'s most cited publications.

```{r}
pubs %>% select(title, author, journal, cites, year) %>% 
  arrange(desc(cites)) %>% slice(1:10) %>% mutate(title = str_to_title(title)) %>% 
  knitr::kable(col.names = c("Title","Author","Journal","Cites","Year"))
```


