---
title: "Google scholar"
output: html_document
params: 
  param_id: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

Vignette for the {scholar} package: https://cran.r-project.org/web/packages/scholar/vignettes/scholar.html



```{r}
library(scholar)
library(tidyverse)
```

Find Google Scholar ID



The example in the vignette was for Richard Feynman, but we need to get a google scholar ID to use the package. I did this by searching "Richard Feynman" in scholar.google.com and clicked through on the author profile. I then copied the url.


https://scholar.google.co.nz/citations?hl=en&user=B7vSqZsAAAAJ

Based on the API lesson we can look at the URL for the profile and the bit after 'user=' should be the ID; B7vSqZsAAAAJ

```{r}
## Define the id for Richard Feynman
#id <- 'B7vSqZsAAAAJ'

if(params$param_id != ""){
  id <- params$param_id
} else {
    id <- 'B7vSqZsAAAAJ'
}

## Get his profile
scholar_profile <- get_profile(id)

# what is contained in a profile?
str(scholar_profile)

## Print his name and affliation
scholar_profile$name
```

So this is telling us some information about the author that google scholar has.

This report is for `r scholar_profile$name`, and is generated on the fly.

We can also get information about his publications

```{r}
pubs <- get_publications(id)

# look at the information for the first 3
head(pubs, 3)
```

We can retrieve information about his citation history

```{r}
## Get his citation history, i.e. citations to his work in a given year
ct <- get_citation_history(id)
```

What does the data we get back look like?

```{r}
head(ct)
```

We can visualise this information by plotting the number of cites (y) by year (x) to see if there is a trend.

```{r}
## Plot citation trend
ggplot(ct, aes(x = year, y = cites)) + geom_line() + geom_point()
```


Users can retrieve the citation history of a particular publication with get_article_cite_history().

We'll use the first publication in the list from get_publications() earlier.
```{r}
head(pubs, 1)
```

We can get the citation history for this particular article with get_article_cite_history(). We need to provide it the author id, and the publication id foe our article of choice
```{r}
## Get article citation history
article_cites <- get_article_cite_history(id, pubs$pubid[1])
```

What is the information we get back?

```{r}
head(article_cites)
```


We can plot this information to see how citiations changed over time for this particular article

```{r}
## Plot citation trend
ggplot(article_cites, aes(x = year, y = cites)) +
    geom_segment(aes(xend = year, yend = 0), size=1, color='darkgrey') +
    geom_point(size=3, color='firebrick')

```

We can also compare authors

```{r}
# Compare Feynman and Stephen Hawking
ids <- c('B7vSqZsAAAAJ', 'qj74uXkAAAAJ')

# Get a data frame comparing the number of citations to their work in
# a given year
cs <- compare_scholars(ids)

## remove some 'bad' records without sufficient information
cs <- filter(cs, !is.na(year) & year > 1900)
ggplot(cs, aes(year, cites, group=name, color=name)) + geom_line() + theme(legend.position="bottom")
```

We can also visualise co-author networks

```{r}
coauthor_network <- get_coauthors('amYIKXQAAAAJ&hl', n_coauthors = 7)

coauthor_network
```

Plot the network
```{r}
plot_coauthors(coauthor_network)
```


A slightly different version of the plot is used in this example https://andreacontina.com/google-scholar/

